{\sc underworlds}: Cascading Situation Assessment for Robots

### 2018-01-24 paper.tex
Updated the formal description section

\usepackage{graphicx}
\usepackage{tikz}
\usetikzlibrary{arrows}
\usepackage{booktabs} % For formal tables

\usepackage{multicol}
\usepackage[bookmarks=true]{hyperref}

@@

\usepackage{amssymb}
\usepackage{amsmath}
\DeclareMathOperator{\transform}{\odot}
\DeclareMathOperator{\filter}{\ominus}
\DeclareMathOperator{\W}{\mathcal{W}}

@@

An \uwds \emph{world} $\W^k$ consists in a pair $\{\mathcal{S}^k,
\mathcal{T}^k\}$.

$\mathcal{S}^k=\{N^k, T^k\}$ is a tree representing a spatial
scene (\emph{scene graph}), with $N^k$ the set of nodes and $T^k$ the set of
transformations between the nodes. $|T^k| = |N^k| - 1$ and $n^k_0 \in N^k$ is
called the root node of the scene $\mathcal{S}^k$.

$\mathcal{T}^k=\{Evt^k, Sit^k\}$ is the world's \emph{timeline}, consisting in a
set $Evt^k$ of events (duration-less states) and a set $Sit^k$ of sitations
(states with a start time and an option end time).

\uwds \emph{transformations} $\transform$ are operators that transform one world into
another. They are often unary operator (for instance, $\mathcal{W}^{k'} =
\transform\mathcal{W}^k$), but do not have to. \emph{Filters} (noted $\filter$)
are a common type of unary, antiextensive transformations such as
$\filter\mathcal{W}^k \subseteq \mathcal{W}^k$.

An \uwds \emph{network} $\mathcal{N} = \{W, O\}$ is a directed graph (cycles are
permitted) of worlds $W=\{\mathcal{W}^k\}, k\in0\ldots n$ and operators
$O=\{\transform^l\}, l \in 0\ldots m$.

\begin{tikzpicture}[->,>=stealth',level/.style={sibling distance = 5cm/#1,
    level distance = 1.5cm}] 
    \node {$\mathcal{W}^0$ {\tt\footnotesize base}}
    child{ node  {$\W^1$ {\tt\footnotesize corrected}} edge from parent node[above left] {$\filter$}
            child{ node {$\W^2$ {\tt\footnotesize semantic\_map}} 
                child{ node {}} %for a named pointer
                            child{ node {}}
            }
            child{ node  {$\W^3$ {\tt\footnotesize post\_planning}}
                            child{ node {}}
                            child{ node {}}
            }                            
    }
    ; 
\end{tikzpicture}

>>>>

\usepackage{graphicx}
\usepackage{tikz}
\usetikzlibrary{graphs,graphdrawing,arrows}
\usegdlibrary{trees, layered}
\usepackage{booktabs} % For formal tables
\usepackage{multicol}
\usepackage[bookmarks=true]{hyperref}

@@

\usepackage{amssymb}
\usepackage{amsmath}
\DeclareMathOperator{\op}{\odot}
\DeclareMathOperator{\filter}{\otimes}
\DeclareMathOperator{\generator}{\oplus}
\DeclareMathOperator{\consumer}{\ominus}
\DeclareMathOperator{\W}{\mathcal{W}}
\DeclareMathOperator{\Ws}{\boldsymbol{W}}
\DeclareMathOperator{\Os}{\boldsymbol{O}}

@@

An \uwds \emph{world} $\W^k \in \Ws$ consists in a pair (\emph{scene}, \emph{timeline}),
noted $\{\mathcal{S}^k,
\mathcal{T}^k\}$.

$\mathcal{S}^k=\{N^k, T^k\}$ is a tree representing a spatial scene (\emph{scene
graph}), with $N^k$ the set of nodes and $T^k$ the set of 6D geometric
transformations between the nodes ($|T^k| = |N^k| - 1$). $n^k_0 \in N^k$ is
called the \emph{root node} of the scene $\mathcal{S}^k$.

$\mathcal{T}^k=\{Evt^k, Sit^k\}$ is the world's \emph{timeline}, consisting in a
set of events $Evt^k$ (duration-less states) and a set of situations $Sit^k$
(states with a start time and an option end time).

\uwds \emph{operators} (noted $\op\colon \Ws^{0\ldots m} \rightarrow
\Ws^{0\ldots n}$) transform one world into another. Examples of operators
include \emph{filters} (noted $\filter$), a common type of unary, antiextensive
transformations such as $\filter\W^k \subseteq \W^k$, and \emph{generators}
(noted $\generator$), a class of nullary operators that are used to create new
worlds (for instance, from perception routines).

Finally, an \uwds \emph{network} $\mathcal{N} = \{\Ws, \Os\}$ is a directed graph (cycles are
permitted) of worlds $\Ws=\{\W^k\}, k\in0\ldots n$ and operators
$\Os=\{\op^l\}, l \in 0\ldots m$. As described in the following sections,
operators are typically implemented as independent software processes that connect at
runtime to their operands, \ie the \uwds worlds, to read and write them. These
processes are hereafter called \emph{clients} of the \uwds network.

%As an example, Figure~\ref{fig|formal-net} shows the
%formal model of the \uwds network represented in Figure~\ref{fig|scene}.
%
%\begin{figure}[!h]
%    \centering
%    \begin{tikzpicture}[nodes={text height=0.4cm,align=center,text width=1.5cm,
%                    draw=black!20, thick, fill=white, font=\footnotesize},
%                        tr/.style={draw=none,text width=0.3cm},
%                        >=stealth', rounded corners, semithick]
%\graph [layered layout, grow=right, level distance=0.5cm, sibling sep=.5em, sibling distance=1cm] {
%    "$\W^0$ {\tiny\tt base}" -- "$\filter^0$"[tr] -> "$\W^1$ {\tiny\tt corrected}";
%        "$\W^1$ {\tiny\tt corrected}" -- "$\op^2$"[tr] -> "$\W^3$ {\tiny\tt post\_planning}";
%        "$\W^1$ {\tiny\tt corrected}" -- "$\op^1$"[tr] -> "$\W^2$ {\tiny\tt semantic\_mapping}";
%};
%\end{tikzpicture}
%\caption{}
%    \label{fig|formal-net}
%\end{figure}
%
